---
output:
  github_document:
    html_preview: false
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

"binomial" is a package that provides functions to calculate the binomial probability distribution functions


### `bin_choose` is a function that computes the number of success in given trials
### `bin_probability` is a function that computes the probability of getting successes in given trials.
### `bin_distribution` is a function that computes the probability distribution.
### `bin_cumulative` is a function that computes the cumulative distribution.
### `bin_variable` is a function that computes the measurement of the variables.
###Functions `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, `bin_kurtosis()` calculate the measurments of the binomial functions.
###`plot.bincum()` method for a "bincum" object to graph the cumulative distribution
###`plot.bindis()` method for a "bindis" object to graphs a barplot to display the probability histogram
###`print.binvar()` method for a "binvar" object to nicely print the content
###`summary.binvar()` method for a "binvar" object to get a full summary description
###`print.summary.binvar()` method for a "summary.binvar" object to nicely print the contents


## Motivation

This package is to provide binomial probability distribution functions that illustrates binomial concepts. 


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}


# development version from GitHub:
#install.packages("devtools") 
#install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-yipszeka/workout03/binomial")
#install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-yipszeka/workout03/binomial", build_vignettes = TRUE)


```


##Usage 

```{r}

library(binomial)

library(ggplot2)

# binomial choose 
bin_choose()

#binomial probability 
bin_probability(1,2,0.6)
#bin_cumulative
w<- bin_cumulative(3,0.1)
w

#binomial distribution
q <- bin_distribution()
q

#plot probability density graph
plot(q)

#plot cumulative graph
plot(w)

#bin_variable
bin_variable(10,0.3)
a <-summary(bin_variable(trials = 10, p = 0.3))
a

```
###Functions of meansures functions
```{r}

library(binomial)

bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)

bin_skewness(10, 0.3)

bin_kurtosis(10, 0.3)


```


